%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemEx}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}

  {\Large \textbf{Yibo Liu}}
  & Email: \href{mailto:yiboliu@asu.edu}{yiboliu@asu.edu} \\

  \small
  \faGithub\ \href{https://github.com/bluesadi}{34r7hm4n}
  \quad
  \faGraduationCap\ \href{https://scholar.google.com/citations?user=Ckof_x4AAAAJ&hl=en}{Google Scholar}
  & \small Mobile: \href{tel:+15052102247}{+1-505-210-2247} \\

\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Tempe, AZ}
      {PhD student in Computer Science, advised by Dr. Ruoyu Wang}{August 2023 -- Present}
    \resumeSubheading
      {Sichuan University}{Chengdu, China}
      {Bachelor in Cybersecurity}{September 2019 -- June 2023}
  \resumeSubHeadingListEnd

\section{Research Interests}
 \resumeSubHeadingListStart
   \resumeItem{Decompilation\vspace{-4pt}}
   \resumeItem{Binary Analysis\vspace{-4pt}}
   \resumeItem{LLM for Security\vspace{-4pt}}
   \resumeItem{Vulnerability Discovery\vspace{-4pt}}
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
 \resumeSubHeadingListStart
\resumeSubheading
  {Shellphish}{Tempe, AZ}
  {Team Member, Reverse Engineering}{August 2023 - Present}
    \resumeItemListStart
      \resumeItem{Participated as a reverse engineer in international CTF competitions, including the DEF CON CTF Finals.}
    \resumeItemListEnd
\resumeSubheading
  {Chinese University of Hong Kong}{Hong Kong SAR, China}
  {Research Assistant, advised by Dr. Sze Yiu Chau}{August 2022 -- December 2022}
  \resumeItemListStart
    \resumeItem{Studied security-critical API misuses in firmware and their implications for software security.}
    \resumeItem{Evaluated state-of-the-art static analysis tools and identified significant inaccuracies and usability limitations.}
    \resumeItem{Analyzed root causes of incorrect reports and co-authored \textit{Towards Precise Reporting of Cryptographic Misuses} (NDSS 2024, second author).}
  \resumeItemListEnd
 \resumeSubheading
      {0x401 Team}{Chengdu, China}
      {Team Member, Reverse Engineering} {October 2020 - June 2023}
      \resumeItemListStart
        \resumeItem{Participated as a reverse engineer in regional and national CTF competitions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------



%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
\resumeSubheading
  {Oxidizer}{}
  {A Rust-oriented Decompiler}{December 2023 - Present}
  \resumeItemListStart
    \resumeItem{
      Conducted an empirical study of Rust-specific decompilation challenges when applying
      state-of-the-art C decompilers to Rust binaries, and identified key language- and
      compiler-induced obstacles.
    }
    \resumeItem{
      Designed a novel Rust decompilation pipeline and implemented multiple techniques to
      address these challenges, providing a foundation for future improvements and extensions.
    }
  \resumeItemListEnd
 \resumeSubheading
      {Pluto}{\href{https://github.com/bluesadi/Pluto}{bluesadi/Pluto}}
      {An obfuscator based on LLVM} {June 2021 - January 2024}
      \resumeItemListStart
        \resumeItem{Pluto converts the source code into a functionally equivalent but much more complicated form at compile-time, protecting your software from being cracked.}
        \resumeItemEx{Data Obfuscaton}{Substitution, String Encryption, Mixed Boolean-Arithmetic Obfuscation}
        \resumeItemEx{Control Flow Obfuscaton}{Flattening, Bogus Control Flow, Indirect Call Obfuscation}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Programming Languages}{: C/C++, Java, Python, Kotlin, Rust}
   }
\item{
  \textbf{Security Skills}{: Decompilation, Reverse Engineering, Program \& Binary Analysis;
  practical experience using tools such as angr and LLVM to solve real-world security problems}
}
 \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\section{Publications}
\resumeSubHeadingListStart

  \resumeItem{
    \textbf{Oxidizer: Toward Concise and High-fidelity Rust Decompilation}.\\
    \textbf{Yibo Liu}, Zion Leonahenahe Basque, Arvind S. Raj, Chavin Udomwongsa,
    Chang Zhu, Jie Hu, Changyu Zhao, Fangzhou Dong, Adam Doup\'e,
    Tiffany Bao, Yan Shoshitaishvili, Ruoyu Wang.\\
    \textit{IEEE Symposium on Security and Privacy (S\&P)}, 2026. (To appear)
  }

  \resumeItem{
    \textbf{BuildBench: Benchmarking LLM Agents on Compiling Real-World Open-Source Software}.\\
    Zehua Zhang, Ati Priya Bajaj, Divij Handa, Siyu Liu, Arvind S. Raj,
    Hongkai Chen, Hulin Wang, \textbf{Yibo Liu}, Zion Basque,
    Souradip Nath, Vishal Juneja, Nikhil Chapre, Yan Shoshitaishvili,
    Adam Doup\'e, Chitta Baral, Ruoyu Wang.\\
    \textit{arXiv preprint}, 2025.
  }

  \resumeItem{
    \textbf{TYGR: Type Inference on Stripped Binaries using Graph Neural Networks}.\\
    Chang Zhu*, Ziyang Li*, Anton Xue, Ati Priya Bajaj, Wil Gibbs, \textbf{Yibo Liu},
    Rajeev Alur, Tiffany Bao, Hanjun Dai, Adam Doup\'e, Mayur Naik,
    Yan Shoshitaishvili, Ruoyu Wang, Aravind Machiry.\\
    \textit{33rd USENIX Security Symposium (USENIX Security)}, 2024.\\
    \textit{(* equal contribution)}
  }

  \resumeItem{
    \textbf{Fuzz to the Future: Uncovering Occluded Future Vulnerabilities via Robust Fuzzing}.\\
    Arvind S. Raj, Wil Gibbs, Fangzhou Dong, Jayakrishna Menon Vadayath,
    Michael Tompkins, Steven Wirsz, \textbf{Yibo Liu}, Zhenghao Hu,
    Chang Zhu, Gokulkrishna Praveen Menon, Brendan Dolan-Gavitt,
    Adam Doup\'e, Ruoyu Wang, Yan Shoshitaishvili, Tiffany Bao.\\
    \textit{ACM SIGSAC Conference on Computer and Communications Security (CCS)}, 2024.
  }

  \resumeItem{
    \textbf{Towards Precise Reporting of Cryptographic Misuses}.\\
    Yuchen Chen, \textbf{Yibo Liu}, Kaiyuan Wu, Duc Van Le, Sze Yiu Chau.\\
    \textit{Network and Distributed System Security Symposium (NDSS)}, 2024.
  }

\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
